Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-03 supp.rnw
Fix incorrect words being pluralised in the partial residual plots' captions.

	partial_residuals_plot <- function(parameters, species_output_order) {
		plot_df <- c()
		for(row_index in 1:num_species) {
			for(col_index in 1:num_species) {
				temp_df <- data.frame(
					y = input_data$get_partial_residuals(parameters, row_index, col_index),
					x = input_data$get_partial_residuals_x(row_index, col_index)
				)
				temp_df$row_index <- rep(row_index, nrow(temp_df))
				temp_df$col_index <- rep(col_index, nrow(temp_df))
				plot_df <- rbind(plot_df, temp_df)
			}
		}

@@

%TODO: Reorder partial residual/model fit plots to use same species order as other figures.
\begin{figure}
	<<echo=FALSE>>=
		plot(model_fit_plot(best_parameters, species_output_order))
	@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(partial_residuals_plot(best_parameters, species_output_order))
	@

	\caption{%
		Partial residuals plot using the most parsimonious model.
	}
	\label{fig:partial-residual-best}
\end{figure}

\begin{figure}
	<<echo=FALSE>>=
		plot(partial_residuals_plot(average_parameters, species_output_order))
	@

	\caption{%
		Partial residuals plot using the model average model.
	}
	\label{fig:partial-residual-average}
\end{figure}

>>>>

	partial_residual_plot <- function(parameters, species_output_order) {
		plot_df <- c()
		for(row_index in 1:num_species) {
			for(col_index in 1:num_species) {
				temp_df <- data.frame(
					y = input_data$get_partial_residuals(parameters, row_index, col_index),
					x = input_data$get_partial_residuals_x(row_index, col_index)
				)
				temp_df$row_index <- rep(row_index, nrow(temp_df))
				temp_df$col_index <- rep(col_index, nrow(temp_df))
				plot_df <- rbind(plot_df, temp_df)
			}
		}

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(model_fit_plot(best_parameters, species_output_order))
	@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(partial_residual_plot(best_parameters, species_output_order))
	@

	\caption{%
		Partial residual plots using the most parsimonious model.
	}
	\label{fig:partial-residual-best}
\end{figure}

\begin{figure}
	<<echo=FALSE>>=
		plot(partial_residual_plot(average_parameters, species_output_order))
	@

	\caption{%
		Partial residual plots using the model average model.
	}
	\label{fig:partial-residual-average}
\end{figure}
